---
title: "k-Means"
author: "Riddhik Rathod"
date: "March 29, 2016"
output: html_document
---

# K-Means Algorithm

* The code below demonstrates the use of the k-means algorithm. 
* K-Means is a part of unsupervised machine learning and thus there is **no training and testing data**.
* K-Means helps forming clusters of the dataset and getting useful insights.


### Implementation in R

The protien.csv dataset is present in the data folder.
```{r}
food = read.csv('./data/protein.csv', header = T)
```

Exploratory data analysis of the variable types
```{r basicconsole}
str(food)
```

Summary of the features of the dataset
```{r}
summary(food)
```

Plot between each variable to visualize data
```{r}
plot(food[,-1])
```

Normalizing the data since the range of all variables is different. 
```{r}
std_data = scale(food[,-1])
```

Running the k-means algorithm on the dataset. The dataset is divided into 7 clusters. 
nstart is the random starting point. Clustering is done for all the random points and the best cluster is taken.
For nstart = 10, 10 different starting points are chosen randomly and the k-means algorithm runs 10 times.
After this, the best k-means solution is chosen among them. 
```{r}
clusters = kmeans(std_data, nstart = 10, centers = 7)
```

Checking the model details. 
```{r}
clusters
```
